% Minimal Working Example: Font Shape Warning in econsocart.cls
% Issue: LaTeX Font Warning: Font shape 'T1/put/m/scit' undefined
% Date: November 4, 2025

\documentclass[qe]{econsocart}

\begin{document}

\begin{frontmatter}
\title{Font Shape Warning Demonstration}
\runtitle{Font Shape Warning Demonstration}

\begin{aug}
\author[add1]{\fnms{Christopher}~\snm{Carroll}\ead[label=e1]{ccarroll@jhu.edu}}
\address[add1]{\orgname{Johns Hopkins University, NBER, and econ-ark.org}}
\end{aug}

\begin{abstract}
This minimal document demonstrates font shape warnings in the \texttt{econsocart.cls} 
document class when using small caps combined with italic emphasis. The document 
compiles successfully but produces warnings about undefined font shapes.
\end{abstract}
\end{frontmatter}

\section{The Problem}

This paragraph contains normal text. Now we demonstrate the issue:

% THIS LINE TRIGGERS THE WARNING:
This text uses \textsc{small caps} and this uses \textit{italic}, 
but combining them as \textsc{\textit{small caps italic}} causes:

\textbf{LaTeX Font Warning: Font shape `T1/put/m/scit' undefined}

The warning occurs because the Utopia font (T1/put) does not define the 
\texttt{scit} font shape (small caps + italic combined). LaTeX substitutes 
an available shape and continues compilation.

\section{Additional Problematic Combinations}

The following font shape combinations are also undefined (each produces warnings):

\begin{itemize}
    \item \texttt{scit}: small caps + italic → \textsc{\textit{produces warning}}
    \item \texttt{scsl}: small caps + slanted → \textsc{\textsl{produces warning}}
    \item \texttt{slit}: slanted + italic → \textsl{\textit{produces warning}}
\end{itemize}

\section{Expected vs. Actual Behavior}

\textbf{Expected}: LaTeX should either:
\begin{enumerate}
    \item Provide the combined font shape, or
    \item Silently substitute a close approximation without warnings
\end{enumerate}

\textbf{Actual}: Compilation succeeds with warnings. LaTeX substitutes available 
shapes but issues warnings about undefined font shapes. The document is generated 
successfully with acceptable typography.

\end{document}

